### 2021-04-30 newvariant.tex
done?

Using the Gamma framework \citep{doi:10.1098/rsif.2020.0144} can help us evaluate these differences more clearly.
For example, \cite{davies2021estimated} estimated a relative strength of $\rho=1.77$ assuming a fixed generation generation interval at 5.5 days from $\delta=0.104\pday$ in one of their regression analysis.
Similarly, \cite{volz2021transmission} estimated $\rho=1.79$ by directly comparing the ratio between $\Rv$ and $\Rw$ assuming a mean generation interval of 6.5 days and a squared coefficient of variation of 0.38.
In this case, the latter study's longer mean generation interval (which increases $\rho$) is counter-balanced by the effects of their wider distribution (which decreases $\rho$).
Instead, if we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.27$ (from $\delta=0.104\pday$ and $\rw = 0\pday$; \cite{davies2021estimated}).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that these estimates of $\rho$ are more accurate.
Instead, this illustrative calculation highlights the importance of propagating uncertainty in generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.

>>>>

Using the Gamma framework \citep{doi:10.1098/rsif.2020.0144} can help us reconcile different estimates more clearly.
For example, \cite{davies2021estimated} estimated a relative strength of $\rho=1.77$ assuming a fixed generation generation interval at 5.5 days from $\delta=0.104\pday$ in one of their regression analysis.
Similarly, \cite{volz2021transmission} estimated $\rho=1.79$ by directly comparing the ratio between $\Rv$ and $\Rw$ assuming a mean generation interval of 6.5 days and a squared coefficient of variation of 0.38.
In this case, the latter study's longer mean generation interval (which increases $\rho$) is counter-balanced by the effects of their wider distribution (which decreases $\rho$).
Instead, if we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.27$ (from $\delta=0.104\pday$ and $\rw = 0\pday$; \cite{davies2021estimated}).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that these estimates of $\rho$ are more accurate.
This illustrative calculation highlights the importance of propagating uncertainty in generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.
